\section*{Conference Presentations}
\noindent

Poldrack RA (2020). \emph{Towards an open science ecosystem for neuroimaging}. Keynote talk presented to the Neuromatch.io conference (virtual).  March. \vspace{2mm} 

Poldrack RA (2020). \emph{Toward an ecosystem for open and reproducible science}. Talk presented to the Max Planck Cognition Academy (virtual).  January. \vspace{2mm} 

Poldrack RA (2019). \emph{Towards an open science ecosystem for neuroimaging}. Talk presented to the Montreal Neurological Institute Open Science Symposium (virtual).  March. \vspace{2mm} 

Poldrack RA (2019). \emph{The importance of standards for data sharing in neuroimaging}. Keynote presented at the Human Connectome Project Investigators Meeting, Bethesda, MD, May. \vspace{2mm} 

Poldrack RA (2019). \emph{OpenNeuro: An open archive for BRAIN Initiative neuroimaging data}. Talk presented at the BRAIN Initiative Investigators Meeting, Washington, DC, April. \vspace{2mm} 

Poldrack RA (2019). \emph{Grand views and potholes on the road to precision neuroimaging}. Talk presented at the Neuroimaging and Modulation in Obesity and Diabetes Research 10th Anniversary Meeting, Bethesday, MD, April. \vspace{2mm} 

Poldrack RA (2019). \emph{Building around standards: The role of BIDS in neuroimaging data sharing}. Talk presented at the ACNN Annual Meeting, Ann Arbor, MI, September. \vspace{2mm} 

Poldrack RA (2019). \emph{OpenNeuro: Data sharing for the BRAIN Initiative}. Talk presented at the OHBM Open Science SIG, Rome, June. \vspace{2mm} 

Poldrack RA (2019). \emph{What's wrong with neuroimaging research, and how can we make it right}. Talk presented at the Neurohackademy, Seattle, WA, June. \vspace{2mm} 

Poldrack RA (2018). \emph{Toward a Computational Ontology of Mental Function}. Keynote presented at the Deliberations on Cognitive Ontology Conference, St. Louis, MO, October. \vspace{2mm} 

Poldrack RA (2018). \emph{How Data Sharing Succeeded in Neuroimaging}. Keynote presented at the SRCD DEVSEC2018 Meeting, Phoenix, AZ, October. \vspace{2mm} 

Poldrack RA (2018). \emph{Reproducibility in neuroimaging: What is the problem}. Talk presented at Neurohackademy 2018, Seattle, July. \vspace{2mm} 

Poldrack RA (2018). \emph{What is the structure of self-regulation}. Talk presented at the Association for Psychological Science Annual Meeting, San Francisco, May. \vspace{2mm} 

Poldrack RA (2018). \emph{From Big Data to Big Knowledge. Analytic and conceptual challenges for developmental neuroimaging}. Talk presented at the FLUX Satellite meeting, Chapel Hill, NC, May. \vspace{2mm} 

Poldrack RA (2018). \emph{Creating a reproducible research pipeline}. Talk presented at the BBSRC STARS Course on Advanced Methods for Reproducible Science, Windsor, UK, April. \vspace{2mm} 

Poldrack RA (2018). \emph{Towards a robust data organization scheme for neuroimaging: the Brain Imaging Data Structure}. Keynote presented at Neuroinformatics 2018, Montreal, August. \vspace{2mm} 

Poldrack RA (2017). \emph{Improving reproducibility of fMRI studies}. Talk presented at the Society for the Study of Ingestive Behavior, Montreal, July. \vspace{2mm} 

Poldrack RA (2017). \emph{Mechanisms of behavioral change}. Talk presented at the Geneva-Princeton Learning Meeting, January. \vspace{2mm} 

Poldrack RA (2017). \emph{Improving the reproducibility of computational research: Cyberinfrastructure for cognitive neuroscience}. Distinguished Lecture, National Science Foundation, Directorate for Computer and Information Science and Engineering., March. \vspace{2mm} 

Poldrack RA (2017). \emph{Building reproducible analysis workflows}. Talk presented at the BBSRC Workshop on Advanced Methods for Reproducible Science. Windsor, UK, March. \vspace{2mm} 

Poldrack RA (2017). \emph{The dynamics of human brain function}. Talk presented at the Neuroscience Workshop Saclay, Paris, June. \vspace{2mm} 

Poldrack RA (2017). \emph{Making neuroimaging more reproducible and transparent}. Talk presented at the International Conference on Cognitive Neuroscience (ICON), Amsterdam, August. \vspace{2mm} 

Poldrack RA (2017). \emph{Computational infrastructure for cognitive neuroscience: The Poldracklab experience}. Talk presented remotely to NeuroComp17, Madison, WI, August. \vspace{2mm} 

Poldrack RA (2017). \emph{Reproducibility in neuroimaging: Challenges and solutions}. Kavli Workshop Lecture, Society for Neuroeconomics, Toronto, October. \vspace{2mm} 

Poldrack RA (2017). \emph{Making neuroimaging more reproducible and transparent}. Talk presented at the Annual Meeting of the American Academy of Adolescent and Child Psychiatry, Washington, DC, October. \vspace{2mm} 

Poldrack RA (2017). \emph{Reproducibility in neuroimaging: What's the problem}. Talk presented at NeuroHackWeek 2017, Seattle, September. \vspace{2mm} 

Poldrack RA (2016). \emph{Automatic influences on value}. Talk presented at Decision Neuroscience Annual Meeting, Philadelphia, June. \vspace{2mm} 

Poldrack RA (2016). \emph{Using neuroscience to refine the ontology of psychology}. Talk presented at Rethinking the Taxonomy of Psychology, London, Ontario, April. \vspace{2mm} 

Poldrack RA (2016). \emph{Changing choices and preferences through automatic mechanisms}. Talk presented at Association for Psychological Science Annual Meeting, Chicago, May. \vspace{2mm} 

Poldrack RA (2016). \emph{Representing Knowledge in Psychology: Challenges and Perspectives}. Talk presented at Association for Psychological Science Annual Meeting, Chicago, May. \vspace{2mm} 

Poldrack RA (2016). \emph{Inferring mental states from imaging data: OpenfMRI and the Cognitive Atlas}. Talk presented at the Organization for Human Brain Mapping Annual Meeting, Geneva, June. \vspace{2mm} 

Poldrack RA (2016). \emph{The future of fMRI in cognitive neuroscience}. Talk presented at the UCLA Advanced Neuroimaging Summer School. July. \vspace{2mm} 

Poldrack RA (2016). \emph{ Improving the reproducibility of neuroimaging research}. Talk presented at Neurohackweek, Seattle, September. \vspace{2mm} 

Poldrack RA (2015). \emph{The future of fMRI in cognitive neuroscience}. Talk presented at the UCLA Advanced Neuroimaging Summer School. \vspace{2mm} 

Poldrack RA (2015). \emph{Cognitive ontologies, data sharing, and reproducibility. }. Talk presented at the Dagstuhl Perspectives Workshop on Digital Scholarship and Open Science in Psychology and the Behavioral Sciences, Dagstuhl, Germany, July. \vspace{2mm} 

Poldrack RA (2015). \emph{Peripheral gene expression and brain function}. Talk presented at the Organization for Human Brain Mapping Annual Meeting, Honolulu, June. \vspace{2mm} 

Poldrack RA (2015). \emph{Decision making and cognitive control: Towards a new synthesis}. Talk presented at the Nutritional Neuroscience Symposium, Utrecht, Netherlands, March. \vspace{2mm} 

Poldrack RA (2014). \emph{The Cognitive Atlas Project}. Talk presented at the Annual Meeting of the Association for Psychological Science, San Francisco, May. \vspace{2mm} 

Poldrack RA (2014). \emph{Towards a personalized cognitive neuroscience: The MyConnectome Project}. Keynote address presented at the International Conference on Cognitive Neuroscience (ICON), Brisbane, July. \vspace{2mm} 

Poldrack RA (2014). \emph{Large-scale decoding of neurocognitive organization}. Keynote address presented at the Pattern Recognition in Neuroimaging meeting, Tubingen, Germany, June. \vspace{2mm} 

Poldrack RA (2014). \emph{Using neuroimaging to infer mental states: A guided tour through the minefield}. Kavli Foundation Workshop, Society for Neuroeconomics Annual Meeting, Miami, September. \vspace{2mm} 

Poldrack, RA (2014). \emph{Toward an ecosystem for task fMRI data sharing: Neurosynth, Neurovault, and OpenfMRI}. Talk presented at the American Academy of Child and Adolescent Psychiatry, San Diego, October. \vspace{2mm} 

Poldrack RA (2013). \emph{Is ``efficiency'' a useless concept}. Talk presented at the First Flux Congress, Pittsburgh, September. \vspace{2mm} 

Poldrack RA (2013). \emph{Beyond the GLM: Advanced fMRI analysis techniques}. Talk presented at the QBIN Summer School on Basic and Advanced fMRI, August. \vspace{2mm} 

Poldrack RA (2013). \emph{The Cognitive Atlas Project}. Keynote address presented at the Cognitive Ontologies meeting, Manchester, June. \vspace{2mm} 

Poldrack RA (2013). \emph{From neuroimaging to mental structure}. Keynote address presented at the Organization for Human Brain Mapping Annual Meeting, Seattle, June. \vspace{2mm} 

Poldrack RA (2012). \emph{Cognitive Neuroinformatics}. Keynote address presented at Neuroinformatics 2012, Munich, September. \vspace{2mm} 

Poldrack, RA (2012). \emph{The future of fMRI in the cognitive neuroscience of language}. Talk presented at the International Workshop on Brain, Cognition, and Learning, Beijing, June. \vspace{2mm} 

Poldrack, RA (2011). \emph{Learning and changing habits}. Talk presented at the International Workshop on Brain, Cognition, and Learning, Beijing, May. \vspace{2mm} 

Poldrack, RA (2010). \emph{Inference and Imaging}. Talk presented at the Hastings Center Workshop on Interpreting Neuroimages II, Philadelphia, February. \vspace{2mm} 

Miller E, Seppa C, Kittur A, Sabb F,  Poldrack RA (2010). \emph{The Cognitive Atlas: employing interaction design processes to facilitate collaborative ontology creation}. Talk presented to the HCLS 2010 Meeting on The Future of the Web for Collaborative Science, Raleigh, NC, April. \vspace{2mm} 

Poldrack, RA (2010). \emph{Toward a semantic infrastructure for cognitive neuroscience: The Cognitive Atlas}. Talk presented at the Cognitive Neuroscience Society Annual Meeting, Montreal, April. \vspace{2mm} 

Poldrack, RA (2009). \emph{Reading mental states from neuroimaging data: From reverse inference to pattern classification}. Talk presented at the UC Irvine Institute for Mathematical Behavioral Sciences workshop on Inference and Imaging, November. \vspace{2mm} 

Poldrack, RA (2009). \emph{Reading mental states from neuroimaging data: From reverse inference to pattern classification}. Keynote lecture presented at Conceptual Issues in fMRI Interpretation: An Interdisciplinary Workshop, Guelph, Ontario, May. \vspace{2mm} 

Poldrack, RA (2009). \emph{What can we predict from fMRI. Lessons for developmental neuroimaging}. Talk presented at the Conference on Methods and Challenges in Developmental Neuroimaging, Amsterdam, May. \vspace{2mm} 

Poldrack, RA (2008). \emph{Beyond Phrenology: Neuroimaging and cognitive ontologies}. Talk presented at the Annual Meeting of the Organization for Human Brain Mapping, Melbourne, Australia. \vspace{2mm} 

Poldrack, RA (2008). \emph{Neural systems for learning and controlling skills}. Talk presented at the Georgetown CBBC Workshop on The Neurocognition of Language and Memory: Retention, Attrition, and Aging, March. \vspace{2mm} 

Poldrack, RA  Fox, CR (2008). \emph{Prospect theory and the brain}. Talk presented at the NYU Neuroeconomics conference, January. \vspace{2mm} 

Poldrack, RA (2007). \emph{Distinguishing category versus response learning using a reversal paradigm. }. Talk presented at the Memory Disorders Research Society Annual Meeting, Cambridge, England, September. \vspace{2mm} 

Poldrack, RA (2007). \emph{What can (and can\~Ot) fMRI tell us about the brain}. Talk presented at the California Science and the Law Institute Conference on Neurobiology and the Courts. Riverside, CA. \vspace{2mm} 

Poldrack, RA (2007). \emph{Memory systems and category learning}. Talk presented at the European Conference on Visual Perception, Arezzo, Italy, August. \vspace{2mm} 

Poldrack, RA (2006). \emph{Skill acquisition, multiple memory systems, and cognitive control}. Talk presented at the Rodin Remediation Academy Annual Meeting, Georgetown University, October. \vspace{2mm} 

Poldrack, RA (2006). \emph{Learning-related changes during skill learning: Evidence for memory system interactions}. Talk presented at the at the Marburg Conference on Neuroimaging and  Theories of Memory, Marburg, Germany,  July. \vspace{2mm} 

Poldrack RA (2006). \emph{Imaging skill learning using fMRI: Insights and challenges}. Talk presented at the John Merck Fund Summer Institute on the Biology of Developmental Disabilities, Princeton, June. \vspace{2mm} 

Poldrack, RA (2006). \emph{Balancing risk and reward in decision making: An fmri study of the Balloon Analog Risk Task}. Talk presented at the Affect, Motivation, and Decision Making Conference, Ein Boqeq, Israel. \vspace{2mm} 

Poldrack, RA (2005). \emph{Methodological and conceptual challenges for developmental fMRI}. Talk presented at the Amsterdam Conference on Developmental Cogntiive Neuroscience, Amsterdam. \vspace{2mm} 

Poldrack, RA (2005). \emph{The development of phonological awareness}. Talk presented at the Amsterdam Conference on Developmental Cogntiive Neuroscience, Amsterdam. \vspace{2mm} 

Poldrack, R A (2005). \emph{The organization of cognitive functions in the left inferior prefrontal cortex}. Talk presented at the Cognitive Neuroscience Society Annual Meeting, New York. \vspace{2mm} 

Poldrack, R A (2003). \emph{Neural systems for rapid naming and phonological awareness}. Talk presented at the International Dyslexia Association annual meeting, San Diego. \vspace{2mm} 

Poldrack, R A (2003). \emph{Interactive memory systems in humans}. Talk presented at the SFN Pre-Symposium on Interactive Memory Systems, New Orleans. \vspace{2mm} 

Poldrack, R A (2002). \emph{ The role of the basal ganglia in category learning}. Talk presented at the First Cognitive Neuroscience of Category Learning Conference, New York. \vspace{2mm} 

Poldrack, R A (2002). \emph{Functional imaging of of classification learning}. Talk presented at the NIPS Workshop on Foundations and Modeling in Neuroimaging, Whistler, BC. \vspace{2mm} 

Poldrack, R A (2002). \emph{The neural basis of skill learning}. Talk presented at the Memory Disorders Research Society Annual Meeting, San Francisco. \vspace{2mm} 

Poldrack, R A (2001). \emph{Reading and the brain: New directions for diagnosis and treatment}. Talk presented at the 17th Annual Learning Differences Conference, Cambridge, MA. \vspace{2mm} 

Poldrack, R A (2001). \emph{The neural basis of reading and dyslexia: Evidence from magnetic resonance imaging}. Talk presented at the fourth Annual Japanese-American Frontiers in Science Symposium, Tokyo, Japan. \vspace{2mm} 

Poldrack, R A (2001). \emph{Imaging of perceptual and cognitive skill learning}. Talk presented at the Third Annual International Conference on Memory, Valencia, Spain. \vspace{2mm} 

Poldrack, R A (2000). \emph{fMRI studies of striatal and medial temporal lobe activation during category learning}. Talk presented at the Memory Disorders Research Society Annual Meeting, Toronto. \vspace{2mm} 

Poldrack, R A (2000). \emph{A neural basis for reading skill: Evidence from microstructural brain imaging}. Talk presented at the National Dyslexia Research Foundation Annual Conference, Elounda, Greece. \vspace{2mm} 

Poldrack, R A (2000). \emph{Brain Structure and Function: The Relation to Reading}. Talk presented at the BrainConnection.com Brain Research and Learning Conference, San Francisco. \vspace{2mm} 

Poldrack, R A (1998). \emph{Multiple functional roles of the left inferior prefrontal cortex: Evidence from neuroimaging}. Talk presented at the Academy of Aphasia Annual Meeting, November 1998, Santa Fe, NM. \vspace{2mm} 

